A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Caption

\begin{figure}[t]
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{Size of the search space for \McSplit versus CP-FC on the
    labelled, directed, unconnected instances which were solved within the
    timeout by both algorithms.}
    \label{figure:33ved-james-versus-cp-fc-nodes-scatter}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-sip-james-versus-kdown-nodes-scatter.pdf}
    \caption{SIP instances, James vs kdown, Nodes (TODO?? heatmapify this and exclude
    timeouts)}\label{figure:sip-james-versus-kdown-nodes-scatter}
\end{figure}

@@

We have yet to fully investigate variable and value ordering heuristics, i.e.\ the selection of a label class and the selection of a vertex from that label class.
There is also the potential to branch on both sides, that is instead of branching on vertices in $\V(G)$, it would be equally valid to branch on
a vertex in $\V(H)$ , since our data structure treats the
two graphs symmetrically. More interestingly, we could choose which graph to branch on
at each search node using some heuristic (perhaps choosing based on whether the $P$ or
$T$ set is smaller), so long as we can ensure that the search remains complete.

>>>>

\begin{figure}[t]
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{Size of the search space for \McSplit\ versus CP-FC on the
    labelled, directed, unconnected instances which were solved within the
    timeout by both algorithms.}
    \label{figure:33ved-james-versus-cp-fc-nodes-scatter}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-sip-james-versus-kdown-nodes-scatter.pdf}
    \caption{Size of the search space for \McSplit$\downarrow$\ versus $k\downarrow$ on the
    large subgraph isomorphism instances which were solved within the
    timeout by both algorithms.}\label{figure:sip-james-versus-kdown-nodes-scatter}
\end{figure}

@@

We have yet to fully investigate variable and value ordering heuristics, i.e.\ the selection of a label class and the selection of a vertex from that label class.
There is also the potential to branch on both sides, that is instead of branching on vertices in $\V(G)$, it would be equally valid to branch on
a vertex in $\V(H)$, since our data structure treats the
two graphs symmetrically. More interestingly, we could choose which graph to branch on
at each search node using some heuristic (perhaps choosing based on whether the $P$ or
$T$ set is smaller), so long as we can ensure that the search remains complete.
